Paper Figure Generation

### 2023-04-05 R/PaperFigureGeneration.rmd
Small paper figure update
Changed the read length range for figure 6B

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative CC>TT Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
```
```{r figure_6C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

>>>>

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps TGG-Filtered CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered,
#                                          yAxisLabel = "Relative CC>TT Frequency")
```
```{r figure_6B, fig.width = 5, fig.height = 5}
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDCCtoTTSeqFreqAllReps1hFiltered,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT 3' Anchored HYV Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "HYV Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("333"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 24, endBasedBackgroundNum = 6,
                        endBasedCheckPositions = -9, displayPValue = FALSE, xAxisLabel = "Mismatch Relative Position",
                        xAxisOffset = 1, xAxisBreaks = c(-2,-10,-20,-30), xlim = c(-35,-4))
```
```{r figure_6C, fig.width = 7.5, fig.height = 5}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDCCToTTGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDCCToTTGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered CC>TT Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))
